---
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
params:
  pkgname: pkgname
  set_title: report_title
  from: from
  to: to
  gh: gh
title: "`r params$set_title`"      
---

```{r setup, include=FALSE}
library(flexdashboard)
```

```{r}
## Get user data
pkgname <- params$pkgname
from_date <- params$from
to_date <- params$to
gh <- params$gh

library(cranlogs)
library(dplyr)
library(ggplot2)
library(purrr)
library(ggiraph)
do.call(library, args = list("package" = pkgname))

date_diff <- as.Date(to_date, "%Y-%m-%d") - as.Date(from_date, "%Y-%m-%d")

cran_df <-
  cranlogs::cran_downloads(
  packages = pkgname,
  from = from_date,
  to = to_date
  )

cran_summary <-
  cran_df %>%
  summarise(
    min_count = min(count, na.rm = TRUE),
    max_count = max(count, na.rm = TRUE),
    mean_count = mean(count, na.rm = TRUE),
    max_date = max(date, na.rm = TRUE)
  )

# custom environment for package
env_pkg <- loadNamespace(pkgname)

# get full list of function names
fnc_str <-
  Filter(
  f = function(x, p = env_pkg){
    (is.function(get(x, p))
     # Exclude Reference Class object generators for now
     & !methods::is(get(x, p), "refObjectGenerator")
    )
  }
  , x = names(env_pkg)
)

# package dependencies
pkg_deps <- recursive_dependencies(package = pkgname, db = NULL)

# github owner/repository
gh_owner <- gsub(pattern = "/.+", replacement = "", x = gh)
gh_repos <- gsub(pattern = ".+/", replacement = "", x = gh)

# Open pull requests

if(is.null(gh)){
  
  gh_opr <- "N/A"
  
} else {
  
  gh_pr_df <- get_gh_pr(
    owner = gh_owner,
    repo = gh_repos
    )
  
  gh_opr <- gh_pr_df %>%
    filter(state == "open") %>%
    nrow()
}


# Open issues

if(is.null(gh)){
  
  gh_ois <- "N/A"
  
} else {
  
  gh_iss_df <- get_gh_issues(
    owner = gh_owner,
    repo = gh_repos
    ) 
  
  gh_ois <- gh_iss_df %>%
    filter(state == "open") %>%
    nrow()
}
```

Package description {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

### KPI - 1

```{r}
cran_df %>%
  summarise(count = sum(count, na.rm = TRUE)) %>%
  pull(count) %>%
  flexdashboard::valueBox(
    caption = "Total CRAN downloads over period",
    color = "primary"
  )
```

### KPI - 2

```{r}
cran_df %>%
  summarise(count = mean(count, na.rm = TRUE)) %>%
  pull(count) %>%
  round(digits = 1) %>%
  flexdashboard::valueBox(
    caption = "Daily CRAN downloads",
    color = "success"
  )
```

### KPI - 3

```{r}
fnc_str %>%
  length() %>%
  flexdashboard::valueBox(
    caption = "Total number of functions",
    color = "info"
  )
```

Row
-----------------------------------------------------------------------

### KPI - 4

```{r}
pkg_deps %>%
  length() %>%
  flexdashboard::valueBox(
    caption = "Package dependencies",
    color = "warning"
  )
```

### KPI - 5
```{r}
gh_opr %>%
  flexdashboard::valueBox(
    caption = "Open pull requests",
    color = "danger"
  )
```  

### KPI - 6

```{r}
gh_ois %>%
  flexdashboard::valueBox(
    caption = "Open issues",
    color = "#224e87"
  )
```  

Row
-----------------------------------------------------------------------

### Summary

```{r}
# Package description
desc <- utils::packageDescription(pkg = pkgname)

dplyr::tibble(
  Field = names(desc),
  Values = unlist(desc)
) %>%
  DT::datatable(
    extensions = c('Buttons',
                   'FixedColumns'),
             options = list(dom = 'lfrtip',
                            fixedColumns = list(leftColumns = 2),
                            scrollX = TRUE,
                            lengthMenu = list(c(-1, 10,25,50),
                                              c("All", 10,25,50))))
```

CRAN Download Stats
=======================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Graph

```{r}
cran_g <-
  cran_df %>%
  ggplot(aes(x = date, y = count)) +
  geom_line_interactive(size = 1, colour = "#224e87") +
  geom_point_interactive(aes(tooltip = count), colour = "#224e87") +
  
  # average line --------------------------------------------------
  geom_hline_interactive(yintercept = mean(cran_df$count),
             colour = "red",
             linetype = 2) + # Average line
  geom_text(
    data = cran_summary,
    aes(y = mean_count,
        x = max_date,
        label = paste("Daily average:", round(mean_count, 1))),
    vjust = 1.2,
    hjust = 0.8,
    size = 3,
    colour = "red") +
  # max line -------------------------------------------------------
  geom_hline_interactive(yintercept = cran_summary$max_count,
             colour = "grey20",
             linetype = 2) + # Average line
  geom_text(
    data = cran_summary,
    aes(y = max_count,
        x = max_date,
        label = paste("Daily max:", max_count)),
    vjust = 1.2,
    hjust = 0.8,
    size = 3,
    colour = "grey20") +
  labs(
    title = paste0(pkgname, ": CRAN Package Downloads over the past ",
                   as.numeric(date_diff), " days"),
    subtitle = paste("From", min(cran_df$date),
                     "to", max(cran_df$date)),
    y = "Downloads",
    x = "Date"
  )

ggiraph::girafe(ggobj = cran_g)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Table

```{r}
DT::datatable(cran_df,
             extensions = c('Buttons',
                            'FixedColumns'),
             options = list(dom = 'Blfrtip',
                            fixedColumns = list(leftColumns = 2),
                            scrollX = TRUE,
                            buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                            lengthMenu = list(c(-1, 10,25,50),
                                              c("All", 10,25,50))))
```

Function Summary
=======================================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Table

```{r}
fs_df <- generate_summary(package_name = pkgname)

DT::datatable(fs_df,
             extensions = c('Buttons',
                            'FixedColumns'),
             options = list(dom = 'Blfrtip',
                            fixedColumns = list(leftColumns = 2),
                            scrollX = TRUE,
                            buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                            lengthMenu = list(c(-1, 10,25,50),
                                              c("All", 10,25,50))))
```

Package dependencies
=======================================================================

Column
-----------------------------------------------------------------------

```{r}
dependencyList <- tools::package_dependencies(
  pkg_deps,
  reverse = FALSE,
  recursive = FALSE,
  db = NULL,
  which = c("Depends", "Imports")
)

dependencyList <- Filter(function(x){!is.null(x)}, dependencyList)

# If pkg A depends on pkg B, then A -> B
# A is the SOURCE and B is the TARGET
# This is UML dependency convention
edges <- names(dependencyList) %>%
  purrr::map(function(x){
    dplyr::tibble(
      SOURCE = rep(x, length(dependencyList[[x]])),
      TARGET = dependencyList[[x]]
    )}) %>%
  bind_rows()

# Get and save nodes
nodes <- data.table::data.table(
  node = unique(
    c(
      edges$SOURCE,
      edges$TARGET
    )
  )
)
```

### Package dependencies

```{r}
nodes_df <-
  nodes %>%
  mutate(id = node) %>%
  rename(label = "node")

edges_df <-
  edges %>%
  rename(from = "SOURCE",
         to = "TARGET")

visNetwork::visNetwork(nodes_df, edges_df, width = "100%") %>%
  visNetwork::visEdges(arrows = "from")
```

Pull Requests
=======================================================================

Column {data-width=200}
-----------------------------------------------------------------------

### About

The table shows the pull requests that have been created, closed, or merged
during the reporting period.


Column {data-width=800}
-----------------------------------------------------------------------

### Active pull requests

```{r}
if(is.null(gh)){
  
  gh_out <- md2html("Data unavailable as no GitHub repository is provided/available.")
  
} else {
  
  gh_out <- gh_pr_df %>%
      select(
        number,
        title,
        state,
        user,
        created_at,
        closed_at,
        merged_at
        ) %>%
    filter(between(
      created_at,
      as.Date(from_date, "%Y-%m-%d"),
      as.Date(to_date, "%Y-%m-%d")
    ) |
      between(
        closed_at,
        as.Date(from_date, "%Y-%m-%d"),
        as.Date(to_date, "%Y-%m-%d")
      ) |
      between(
        merged_at,
        as.Date(from_date, "%Y-%m-%d"),
        as.Date(to_date, "%Y-%m-%d")
      )
      )
  
  gh_out <-
    DT::datatable(gh_out,
             extensions = c('Buttons',
                            'FixedColumns'),
             options = list(dom = 'Blfrtip',
                            fixedColumns = list(leftColumns = 2),
                            scrollX = TRUE,
                            buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                            lengthMenu = list(c(-1, 10,25,50),
                                              c("All", 10,25,50))))
    
  
}

gh_out

```

Issues
=======================================================================

Column {data-width=200}
-----------------------------------------------------------------------

### About

The table shows the issues that have been created or closed during the reporting
period.


Column {data-width=800}
-----------------------------------------------------------------------

### Active issues

```{r}
if(is.null(gh)){
  
  gh_out <- md2html("Data unavailable as no GitHub repository is provided/available.")
  
} else {
  
  gh_out <- gh_iss_df %>%
      select(
        number,
        title,
        state,
        assignee = "user.login",
        created_at,
        closed_at
        ) %>%
    filter(between(
      created_at,
      as.Date(from_date, "%Y-%m-%d"),
      as.Date(to_date, "%Y-%m-%d")
    ) |
      between(
        closed_at,
        as.Date(from_date, "%Y-%m-%d"),
        as.Date(to_date, "%Y-%m-%d")
      ))
  
  gh_out <-
    DT::datatable(gh_out,
             extensions = c('Buttons',
                            'FixedColumns'),
             options = list(dom = 'Blfrtip',
                            fixedColumns = list(leftColumns = 2),
                            scrollX = TRUE,
                            buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                            lengthMenu = list(c(-1, 10,25,50),
                                              c("All", 10,25,50))))
    
  
}

gh_out

```

